Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex
minor changes to genus 0 base cases

\ssec{Genus 1 base cases}

Let $\sx$ be a tame, seperably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fixed points, and $R_1,\ldots, R_n$ be points on $\sx$. In this section, will compute the canonical ring $R_L$ in the cases that
\begin{enumerate}
	\item $L = 0$
	\item $L = P-Q$
	\item $L = P - Q + \frac{1}{3}R$
	\item $L = P - Q + \frac{e-1}{2e}R, e > 3, e \equiv 1 \bmod 2$ 
	\item $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3$
\end{enumerate}
In addition to being illustrative examples, these will serve as the base cases of induction, in order to compute generators and relations for an arbitrary genus 1, stacky log half canonical divisor. In each of the following examples, we will give explicit generators and relations, and in case $(3)$ and $(4)$ we check the corresponding signature is admissible.

\begin{example}
\label{eg:g_1_triv}
In the case $L = 0,$ we see immediately that $R_L \cong k[x]$ with $x$ a generator in degree 1.
\end{example}

>>>>

\ssec{Genus 1 Base Cases}

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values

\begin{enumerate}
	\item $\halfcan' = 0$
	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3.$
\end{enumerate}

\begin{example}
\label{eg:g_1_triv}
In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
\end{example}

\begin{example}
Let $\sx$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$. Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.

Here, we claim $R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k.$

 and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.

\todo{check admissibility}
\end{example}

\todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
Let $\sx$ be a tame, seperably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fixed points, and $R_1,\ldots, R_n$ be points on $\sx$. In this section, will compute the canonical ring $R_{\halfcan'}$ in the cases that
\begin{enumerate}
	\item $\halfcan' = P-Q$
	\item $\halfcan' = 0$
	\item $\halfcan' = P-Q$
	\item $\halfcan' = P - Q + \frac{1}{3}R$
	\item $\halfcan' = P - Q + \frac{e-1}{2e}R, e > 3, e \equiv 1 \bmod 2$ 
	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3$
\end{enumerate}
In addition to being illustrative examples, these will serve as the base cases of induction, in order to compute generators and relations for an arbitrary genus 1, stacky log half canonical divisor. In each of the following examples, we will give explicit generators and relations, and in case $(3)$ and $(4)$ we check the corresponding signature is admissible.
